---
title: "lab_6"
author: "Sam Rozal"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)

```

## Example of a rank-based test

we'll make our own samples usinga pseudorandom generator.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size=15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test:
```{r}
t.test(gp_1,gp_2)

```
What is the meaning of the p-value?

If these samples were drawn from two poulatosn with the same mean, the probabilty of taking two random samples with means *at least ad s differnce * as the sample means we found by random chance (taking intoaccount spread, n) is 1 19.8 percent 

Retai (rail to reject) the nul hypothesis. >> There is no signifcant differnce in means between group 1 and group 2

Warning: people get weirdly upset if you say "accept" the null

Now lets compare this outcome to a rank based test. 

## Mahn Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

 What does the p-value mean?
 
If the samples were drawn from populations with the same ranks, then the probability of finding two samples  with ranks *at least as differnt* as those in or samples is 0.28. 

There is no signifcant differnce in ranks (often you'll see medians) between group 1 and group 2 (staistcal summary).

Median scores for group 1 (M= 14) and group 2 (M=12) did not differ signifcantly (Mann Whitney U Test: U(df) = 86, p=0,28).

