---
title: "lab_6"
author: "Sam Rozal"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)

```

## Example of a rank-based test

we'll make our own samples usinga pseudorandom generator.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size=15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test:
```{r}
t.test(gp_1,gp_2)

```
What is the meaning of the p-value?

If these samples were drawn from two poulatosn with the same mean, the probabilty of taking two random samples with means *at least ad s differnce * as the sample means we found by random chance (taking intoaccount spread, n) is 1 19.8 percent 

Retai (rail to reject) the nul hypothesis. >> There is no signifcant differnce in means between group 1 and group 2

Warning: people get weirdly upset if you say "accept" the null

Now lets compare this outcome to a rank based test. 

## Mahn Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

 What does the p-value mean?
 
If the samples were drawn from populations with the same ranks, then the probability of finding two samples  with ranks *at least as differnt* as those in or samples is 0.28. 

There is no signifcant differnce in ranks (often you'll see medians) between group 1 and group 2 (staistcal summary).

Median scores for group 1 (M= 14) and group 2 (M=12) did not differ signifcantly (Mann Whitney U Test: U(df) = 86, p=0,28).

cam put this in the console to check
?wilcox.test
mwu&p.value

## Linear Regression

Simple linear regression (single dependant vaianle, a single independant variable)

```{r}
#Make an exploratory plot of penguin body mass (y-axis) versus fliper length (x-axis)

ggplot(data=penguins, aes(x=flipper_length_mm, y=body_mass_g)) +
  geom_point() +
  geom_smooth(method="lm")
```

Find a linear regression model using ordinary least squares describing the relationship between flipper lengtha nd body mass for these penguins. 


3 pieces :

- What type of model?
- What is teh relationship to model (DV~ IV(s))
- , fWhere is the data that is used  create this model 

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data= penguins)
```


Call:
lm(formula = body_mass_g ~ flipper_length_mm, data = penguins)

Coefficients:
      (Intercept)  flipper_length_mm  
         -5780.83              49.69  
         

penguin_lm$coefficients
      (Intercept) flipper_length_mm 
      -5780.83136          49.68557 
penguin_lm$coefficients[2]
flipper_length_mm 
         49.68557 
         
         
### broom package retyens model outputs as tiny data frames
```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy

broom::glance(penguin_lm) #talk about these more on wednseday 

```
How can I actually include my model equation in a report?

```{r}
extract_eq(model=penguin_lm, use_coef = TRUE)
```

```{r}
plot(penguin_lm)
```
just testing to see if i can still push and pull after redoing the git token. 
